### 2017-12-17 DASFAA_2018/Gruba/07-rela.tex

The main problem of current approaches for behavior modeling lies in that the model is for either the overall users or a single user.
\cite{IEEEexample:journals/tkdd/ZhangTLLX15, IEEEexample:conf/wsdm/FengW13, IEEEexample:conf/ijcai/ZhangLTCL13} discovered that users' \retg{} behavior is largely influenced by their followees, whereas \cite{IEEEexample:conf/cikm/JiangLSW15} employed matrix decomposition, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} used collaborative filtering methods and \cite{IEEEexample:zhang2015retweet} leveraged statistical models for \retg{} analysis.
\cite{IEEEexample:conf/pakdd/GiatsoglouCSFV15} and \cite{IEEEexample:journals/corr/RanganathMHTL15} focused on identifying whether the \retg{} is fraudulent or of protest.
Whereas our work \sys{} builds the \retg{} model for each user group, instead of the mono model for all users or one model per user.

>>>>

The main problem of current approaches for behavior modeling lies in that the model is for either the overall users or a single user.
\cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13} discovered that users' \retg{} behavior is largely influenced by their followees, whereas \cite{IEEEexample:conf/cikm/JiangLSW15} employed matrix decomposition, \cite{IEEEexample:conf/sigir/JiangLSLLMW16} used collaborative filtering methods and \cite{IEEEexample:zhang2015retweet} leveraged statistical models for \retg{} analysis.
\cite{IEEEexample:conf/pakdd/GiatsoglouCSFV15} and \cite{IEEEexample:journals/corr/RanganathMHTL15} focused on identifying whether the \retg{} is fraudulent or of protest.
Whereas our work \sys{} builds the \retg{} model for each user group, instead of the mono model for all users or one model per user.
